Towards practical dynamic induction control of wind farms: analysis of optimally controlled wind-farm boundary layers and sinusoidal induction control of first-row turbines

### 2018-05-17 revision/reply_to_revs_2.tex
R2C2 (replies + manuscript)

``
.., for which an enhanced recovery was found as discussed above. \textbf{The turbulence intensity $TI \equiv (2k/3  )^{1/2}/(U_x^2+U_y^2+U_z^2)^{1/2}$ at hub height (not shown in the figure) is 10\% at the inlet for both the reference case and the controlled case. The combination of reduced near-wake mean velocities and increased velocity fluctuations in the controlled case increase local $TI$ in the turbine wakes (ranging from $\approx 2$\%-points in the wakes of middle rows to $\approx 12$\%-points in the first and last rows). This increase in turbulence intensity dissipates to below $1$\%-point difference at 10$D$ downstream of the last row.}
''

>>>>

``
.., for which an enhanced recovery was found as discussed above. \textbf{The turbulence intensity $TI \equiv (2k/3  )^{1/2}/U_\infty$ at hub height (not shown in the figure) is 10\% at the inlet for both the reference case and the controlled case. The combination of reduced near-wake mean velocities and increased velocity fluctuations in the controlled case increase local $TI$ in the turbine wakes (ranging from $\approx 2$\%-points in the wakes of middle rows to $\approx 12$\%-points in the first and last rows). This increase in turbulence intensity dissipates to below $1$\%-point difference at 10$D$ downstream of the last row.}
''

### 2018-05-17 revision/revised_WM02.tex
R2C2 (replies + manuscript)

Figure \ref{fig:flowfield_statistics}c shows sideviews of turbulence kinetic energy $k$. The figure shows an increase in turbulence throughout the entire wind farm, spreading to the internal boundary layer above the turbines. Note specifically the sharp increase in turbulence in the core wake region behind the first-row turbine, for which an enhanced recovery was found as discussed above. \revision{The turbulence intensity $TI \equiv (2k/3  )^{1/2}/(U_x^2+U_y^2+U_z^2)^{1/2}$ at hub height (not shown in the figure) is 10\% at the inlet for both the reference case and the controlled case. The combination of reduced near-wake mean velocities and increased velocity fluctuations in the controlled case increase local $TI$ in the turbine wakes (ranging from $\approx 2$\%-points in the wakes of middle rows to $\approx 12$\%-points in the first and last rows). This increase in turbulence intensity dissipates to below $1$\%-point difference at 10$D$ downstream of the last row.}

>>>>

Figure \ref{fig:flowfield_statistics}c shows sideviews of turbulence kinetic energy $k$. The figure shows an increase in turbulence throughout the entire wind farm, spreading to the internal boundary layer above the turbines. Note specifically the sharp increase in turbulence in the core wake region behind the first-row turbine, for which an enhanced recovery was found as discussed above. \revision{The turbulence intensity $TI \equiv (2k/3  )^{1/2}/U_\infty$ at hub height (not shown in the figure) is 10\% at the inlet for both the reference case and the controlled case. The combination of reduced near-wake mean velocities and increased velocity fluctuations in the controlled case increase local $TI$ in the turbine wakes (ranging from $\approx 2$\%-points in the wakes of middle rows to $\approx 12$\%-points in the first and last rows). This increase in turbulence intensity dissipates to below $1$\%-point difference at 10$D$ downstream of the last row.}
